Continuous developmental change can explain discontinuities in word learning

### 2020-03-20 Analysis/process.Rmd
revisions

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(langcog)
library(ggthemes)
library(lme4)
library(nlstools)
library(MuMIn)
library(purrr)
theme_set(theme_few())
```

@@

@@

model2_val <- c(confint(fit_children_2), Vr_s_ch, Vr_o_ch, model="2", group = "children") %>%
  bind_rows(c(confint(fit_adults_2), Vr_s_ad, Vr_o_ad, model="2", group = "adults"))

>>>>

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
#library(langcog)
library(ggthemes)
library(lme4)
library(nlstools)
library(MuMIn)
library(purrr)
theme_set(theme_few())
```

@@

Stats here

#Is the most difficult condition is at chance?
rand_stat <- d_child_good %>%
  filter(sound_dist == "similar" & concept_dist == "similar")

myVar <- rand_stat$iscorrect
k <- sum(myVar)
n <- length(myVar)

myTest <- binom.test(k,n, 0.5)

rand_plus_stat <- d_child_good %>%
  filter(sound_dist == "similar" & concept_dist == "different")

myVar <- rand_plus_stat$iscorrect
k <- sum(myVar)
n <- length(myVar)

myTest <- binom.test(k,n, 0.5)

both <- d_child_good %>%
  filter(sound_dist == "similar" & (concept_dist == "similar" || concept_dist == "different"))

data_both <- both %>%
  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
         c_dist=ifelse(concept_dist=="similar", -1, 1))

model_both <- glmer(iscorrect ~ c_dist + 
                 (c_dist  | ID), 
               data = data_both, family = binomial())

@@

#model2_val <- c(confint(fit_children_2), Vr_s_ch, Vr_o_ch, model="2", group = "children") %>%
#  bind_rows(c(confint(fit_adults_2), Vr_s_ad, Vr_o_ad, model="2", group = "adults"))

### 2020-03-20 cogsci/cogsci.Rmd
revisions

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(ggthemes)
library(xtable)
options(xtable.comment = FALSE)
library(purrr)
library(readr)
library(ggplot2)
library(langcog)
library(boot)
#library(lazyeval)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
#library(scales)
library(stringr)
library(lmtest)
library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
library(stargazer)
library(lme4)
```

>>>>

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(ggthemes)
library(xtable)
options(xtable.comment = FALSE)
library(purrr)
library(readr)
library(ggplot2)
#library(langcog)
library(boot)
#library(lazyeval)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
#library(scales)
library(stringr)
library(lmtest)
#library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
library(stargazer)
library(lme4)
```

### 2020-03-20 cogsci/cogsci.tex
revisions

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

@@

\section{Introduction}\label{introduction}

@@

\section{Model}\label{model}

\subsection{Probabilistic structure}\label{probabilistic-structure}

@@

\subsection{Inference}\label{inference}

@@

\subsection{Task and model
predictions}\label{task-and-model-predictions}

@@

\section{Experiment}\label{experiment}

@@

\subsection{Methods}\label{methods}

\subsubsection{Participants}\label{participants}

@@

\subsubsection{Stimuli and similarity
rating}\label{stimuli-and-similarity-rating}

@@

\subsubsection{Design}\label{design}

@@

\subsubsection{Procedure}\label{procedure}

@@

\subsection{Results}\label{results}

We first analyzed the results using a mixed-effects logistic regression
with sound distance, object distance and age group as fixed effects, and
with a maximal random effects structure (allowing us to take into
account the full nested structure of our data) (Barr, Levy, Scheepers,
\& Tily, 2013). We found main effects for all the fixed effects in the
regression. For the sound distance, we obtained \(\beta =\) 0.52 (\(p\)
\textless{} 0.001), replicating previous findings. For object distance,
we found \(\beta =\) 0.83 (\(p\) \textless{} 0.001), and this finding
confirms the new prediction of our model. Finally, for the age group, we
obtained \(\beta =\) 0.76 (\(p\) \textless{} 0.001), showing that
performance improves with age.

@@

\section{General Discussion}\label{general-discussion}

@@

\section{References}\label{references}

\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent

\hypertarget{refs}{}
\hypertarget{ref-barr2013}{}
Barr, D., Levy, R., Scheepers, C., \& Tily, H. (2013). Random effects
structure for confirmatory hypothesis testing: Keep it maximal.
\emph{Journal of Memory and Language}, \emph{68}(3).

\hypertarget{ref-carey2009}{}
Carey, S. (2009). \emph{The origin of concepts}. Oxford University
Press.

\hypertarget{ref-dutoit1996}{}
Dutoit, T., Pagel, V., Pierret, N., Bataille, F., \& Van der Vrecken, O.
(1996). The mbrola project: Towards a set of high quality speech
synthesizers free of use for non commercial purposes. In
\emph{Proceedings of ICSLP} (Vol. 3). IEEE.

\hypertarget{ref-engelthaler2017}{}
Engelthaler, T., \& Hills, T. T. (2017). Feature biases in early word
learning: Network distinctiveness predicts age of acquisition.
\emph{Cognitive Science}, \emph{41}.

\hypertarget{ref-fennell2010}{}
Fennell, C., \& Waxman, S. (2010). What paradox? Referential cues allow
for infant use of phonetic detail in word learning. \emph{Child
Development}, \emph{81}.

\hypertarget{ref-hofer2017}{}
Hofer, M., \& Levy, R. (2017). Modeling Sources of Uncertainty in Spoken
Word Learning. In \emph{Proceedings of the 39th Annual Meeting of the
Cognitive Science Society}.

\hypertarget{ref-lewis2013}{}
Lewis, M., \& Frank, M. (2013). An integrated model of concept learning
and word-concept mapping. In \emph{Proceedings of the annual meeting of
the cognitive science society} (Vol. 35).

\hypertarget{ref-pajak2016}{}
Pajak, B., Creel, S., \& Levy, R. (2016). Difficulty in learning
similar-sounding words: A developmental stage or a general property of
learning? \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{42}(9).

\hypertarget{ref-piaget1954}{}
Piaget, J. (1954). \emph{The construction of reality in the child}. New
York, NY, US: Basic Books.

\hypertarget{ref-rost2009}{}
Rost, G., \& McMurray, B. (2009). Speaker variability augments
phonological processing in early word learning. \emph{Developmental
Science}, \emph{12}.

\hypertarget{ref-sizemore2018}{}
Sizemore, A. E., Karuza, E. A., Giusti, C., \& Bassett, D. S. (2018).
Knowledge gaps in the early growth of semantic feature networks.
\emph{Nature Human Behaviour}, \emph{2}(9).

\hypertarget{ref-stager1997}{}
Stager, C., \& Werker, J. (1997). Infants listen for more phonetic
detail in speech perception than in word-learning tasks. \emph{Nature},
\emph{388}(6640).

\hypertarget{ref-swingley2007}{}
Swingley, D. (2007). Lexical exposure and word-form encoding in
1.5-year-olds. \emph{Developmental Psychology}, \emph{43}(2).

\hypertarget{ref-thiessen2007}{}
Thiessen, E. (2007). The effect of distributional information on
children's use of phonemic contrasts. \emph{Journal of Memory and
Language}, \emph{56}.

\hypertarget{ref-werker2002}{}
Werker, J., Fennell, C., Corcoran, K., \& Stager, C. (2002). Infants'
ability to learn phonetically similar words: Effects of age and
vocabulary size. \emph{Infancy}, \emph{3}.

\hypertarget{ref-white2013}{}
White, K., Yee, E., Blumstein, S., \& Morgan, J. (2013). Adults show
less sensitivity to phonetic detail in unfamiliar words, too.
\emph{Journal of Memory and Language}, \emph{68}(4).

\hypertarget{ref-wojcik2013}{}
Wojcik, E., \& Saffran, J. (2013). The ontogeny of lexical networks:
Toddlers encode the relationships among referents when learning novel
words. \emph{Psychological Science}, \emph{24}(10).

\hypertarget{ref-yoshida2009}{}
Yoshida, K., Fennell, C., Swingley, D., \& Werker, J. (2009).
14-month-olds learn similar-sounding words. \emph{Developmental
Science}, \emph{12}.

>>>>

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{apacite}

% KM added 1/4/18 to allow control of blind submission

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{model}{%
\section{Model}\label{model}}

\hypertarget{probabilistic-structure}{%
\subsection{Probabilistic structure}\label{probabilistic-structure}}

@@

\hypertarget{inference}{%
\subsection{Inference}\label{inference}}

@@

\hypertarget{task-and-model-predictions}{%
\subsection{Task and model
predictions}\label{task-and-model-predictions}}

@@

\hypertarget{experiment}{%
\section{Experiment}\label{experiment}}

@@

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

@@

\hypertarget{stimuli-and-similarity-rating}{%
\subsubsection{Stimuli and similarity
rating}\label{stimuli-and-similarity-rating}}

@@

\#\#\#Design

@@

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

We first analyzed the results using a mixed-effects logistic regression
with sound distance, object distance and age group as fixed effects, and
with a maximal random effects structure (allowing us to take into
account the full nested structure of our data) (Barr, Levy, Scheepers,
\& Tily, 2013). We found main effects for all the fixed effects in the
regression. For the sound distance, we obtained \(\beta =\) 0.68 (\(p\)
\textless{} 0.001), replicating previous findings. For object distance,
we found \(\beta =\) 0.6 (\(p\) \textless{} 0.001), and this finding
confirms the new prediction of our model. Finally, for the age group, we
obtained \(\beta =\) 0.59 (\(p\) \textless{} 0.001), showing that
performance improves with age.

@@

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}

\noindent

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-barr2013}{}%
Barr, D., Levy, R., Scheepers, C., \& Tily, H. (2013). Random effects
structure for confirmatory hypothesis testing: Keep it maximal.
\emph{Journal of Memory and Language}, \emph{68}(3).

\leavevmode\hypertarget{ref-carey2009}{}%
Carey, S. (2009). \emph{The origin of concepts}. Oxford University
Press.

\leavevmode\hypertarget{ref-dutoit1996}{}%
Dutoit, T., Pagel, V., Pierret, N., Bataille, F., \& Van der Vrecken, O.
(1996). The mbrola project: Towards a set of high quality speech
synthesizers free of use for non commercial purposes. In
\emph{Proceedings of ICSLP} (Vol. 3). IEEE.

\leavevmode\hypertarget{ref-engelthaler2017}{}%
Engelthaler, T., \& Hills, T. T. (2017). Feature biases in early word
learning: Network distinctiveness predicts age of acquisition.
\emph{Cognitive Science}, \emph{41}.

\leavevmode\hypertarget{ref-fennell2010}{}%
Fennell, C., \& Waxman, S. (2010). What paradox? Referential cues allow
for infant use of phonetic detail in word learning. \emph{Child
Development}, \emph{81}.

\leavevmode\hypertarget{ref-hofer2017}{}%
Hofer, M., \& Levy, R. (2017). Modeling Sources of Uncertainty in Spoken
Word Learning. In \emph{Proceedings of the 39th Annual Meeting of the
Cognitive Science Society}.

\leavevmode\hypertarget{ref-lewis2013}{}%
Lewis, M., \& Frank, M. (2013). An integrated model of concept learning
and word-concept mapping. In \emph{Proceedings of the annual meeting of
the cognitive science society} (Vol. 35).

\leavevmode\hypertarget{ref-pajak2016}{}%
Pajak, B., Creel, S., \& Levy, R. (2016). Difficulty in learning
similar-sounding words: A developmental stage or a general property of
learning? \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{42}(9).

\leavevmode\hypertarget{ref-piaget1954}{}%
Piaget, J. (1954). \emph{The construction of reality in the child}. New
York, NY, US: Basic Books.

\leavevmode\hypertarget{ref-rost2009}{}%
Rost, G., \& McMurray, B. (2009). Speaker variability augments
phonological processing in early word learning. \emph{Developmental
Science}, \emph{12}.

\leavevmode\hypertarget{ref-sizemore2018}{}%
Sizemore, A. E., Karuza, E. A., Giusti, C., \& Bassett, D. S. (2018).
Knowledge gaps in the early growth of semantic feature networks.
\emph{Nature Human Behaviour}, \emph{2}(9).

\leavevmode\hypertarget{ref-stager1997}{}%
Stager, C., \& Werker, J. (1997). Infants listen for more phonetic
detail in speech perception than in word-learning tasks. \emph{Nature},
\emph{388}(6640).

\leavevmode\hypertarget{ref-swingley2007}{}%
Swingley, D. (2007). Lexical exposure and word-form encoding in
1.5-year-olds. \emph{Developmental Psychology}, \emph{43}(2).

\leavevmode\hypertarget{ref-thiessen2007}{}%
Thiessen, E. (2007). The effect of distributional information on
children's use of phonemic contrasts. \emph{Journal of Memory and
Language}, \emph{56}.

\leavevmode\hypertarget{ref-werker2002}{}%
Werker, J., Fennell, C., Corcoran, K., \& Stager, C. (2002). Infants'
ability to learn phonetically similar words: Effects of age and
vocabulary size. \emph{Infancy}, \emph{3}.

\leavevmode\hypertarget{ref-white2013}{}%
White, K., Yee, E., Blumstein, S., \& Morgan, J. (2013). Adults show
less sensitivity to phonetic detail in unfamiliar words, too.
\emph{Journal of Memory and Language}, \emph{68}(4).

\leavevmode\hypertarget{ref-wojcik2013}{}%
Wojcik, E., \& Saffran, J. (2013). The ontogeny of lexical networks:
Toddlers encode the relationships among referents when learning novel
words. \emph{Psychological Science}, \emph{24}(10).

\leavevmode\hypertarget{ref-yoshida2009}{}%
Yoshida, K., Fennell, C., Swingley, D., \& Werker, J. (2009).
14-month-olds learn similar-sounding words. \emph{Developmental
Science}, \emph{12}.

\bibliographystyle{apacite}
